---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# USPopulationSampler

<!-- badges: start -->
<!-- badges: end -->

The goal of USPopulationSampler is to ...

## Installation

You can install the development version of USPopulationSampler from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jasenzhang1/USPopulationSampler")
```

## Example

```{r}
library(USPopulationSampler)
library(devtools)
load_all()
```

### If we are unsure of the names of the states, we first obtain a list of them

```{r}
get_state_names()
```

### We're interested in all the counties of Tennessee, so we get their county FIPS

```{r}
tennessee_fips <- get_county_fips('Tennessee')
```

### Now we sample at the block-group level for the entire state of Tennessee

```{r}
pts <- US_pop_sampler(N = 1000, tennessee_fips, level = 4)
```

### We prepare shape files of Tennessee as a state and its county borders

```{r}
shape_state <- sampled_region_outline(tennessee_fips, 1)
shape_county <- sampled_region_outline(tennessee_fips, 2)
```

### And we plot our sampled points

```{r}
ps <- 16
cs <- 0.3
alp <- 0.5

par(mfrow = c(1,2))

# plot 1: state border reference
plot(shape_state)
plot(pts, add = T, pch = ps, cex = cs,
       col = rgb(0, 0, 1, alpha = alp))

# plot 2: county border references
plot(shape_county)
plot(pts, add = T, pch = ps, cex = cs,
       col = rgb(0, 0, 1, alpha = alp))
```
